%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Finstek Ltd.} % Organization
    {Minsk, Belarus} % Location
    {Jun. 2023 - Sept. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Together with frontend team, designed and implemented a trading robots SDK proof of concept. During POC stage researched possibilities for crossplatform clientside .NET 7 implementation (Windows, Mac), installers packaging and signing (MSIX, dmg), websockets and REST communication between project parts (Bot manager, Bots, browser-hosted WebTrader app). Developed a possibility to plug a Blazor UI for bots. Additionally developed Bot Market portal backend POC with ability to upload, download and upgrade trading bots to a latest versions.}
        \item {Developed parts of a MembersArea web portal hosted in Azure aimed at forex trader identities management.}
        \item {For TraderPlatform team, designed and developed a .NET 7 microservice to store user-provided chart drawings in SQLite database.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Sababa Labs/Playtika Ltd.} % Organization
    {Minsk, Belarus} % Location
    {Aug. 2019 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In the backend team, migrated .NET 4.5 monolythic gaming backend to microservices. This reduced operational costs by approx. \$2M/year in cloud provider payments by migrating highload gaming backend (600,000 daily active users) from Windows and AWS to Linux and private DC under Kubernetes+Netflix stack (Eureka, Zuul, Hystrix, Ribbon). Used Jenkins and TeamCity as CI/CD, staging/QA/Peprod/Prod environments with canary deployments.}
        \item {Simplified application structure by 10-30\% with integration of Playtika platform Java services into BK: Login, Payments, Journeys, Goods Router, InApps}
        \item {Revamped Minigames feature by extending gaming monolith REST API and its Aerospike storage, resulting in improved user experience and increased monetization. Led a mini-team for the feature, comprising of 2 QA, 2 Unity developers, and myself as a backend developer.}
        \item {Reduced players waiting time and improved tournament experience by implementing a new microservice in .NET Core for custom Journey step (tournament end) based on points instead of tournament ending time.}
        \item {Reimplemented Facebook, Apple, and Guest login based on Playtika services and JWT provider, subsequent optimizations.}
        \item {Served as a gatekeeper for microservices and parts of gaming monolith, as well as some PSF integrations, resulting in a 20\% improvement in problem identification and overall system improvements.}
        \item {Assisted in reducing production incident time by 30\% during on-duty support, monitoring, NOC, and SLS assistance using Prometheus, Grafana, ELK, Kibana, Dynatrace.}
        \item {Developed .NET microservices container healthcheck library to standardize new microservices development}
        \item {Improved team knowledge sharing through several talks and Wiki pages on topics such as Journey messaging debugging assistance during prod incidents, backend architecture overview for onboarding, and containers traffic monitoring in Linux.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {CompatibL LLC} % Organization
    {Minsk, Belarus} % Location
    {Apr. 2008 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented backend part in .NET/.NET Core for accounting and internal assets reporting system for a U.S. bank and stockbroker Charles Schwab.}
        \item {Various custom XVA solution implementations based on Compatibl Analyst platform (Windows and .NET) for major European, U.S. and South African banks.}
        \item {Compatibl Analyst platform extensions, customer data integration business trips (SQL Server, Sybase ASE, Oracle8i).}  
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ScienceSoft Inc.} % Organization
    {Minsk, Belarus} % Location
    {Jan. 2006 - Apr. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a WinForms + SqlServer desktop application for Estonian State Registry Office.}
        \item {Maintained and developed a WinForms production equipment load balancer tool for Baxter Pharmaceuticals.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {VPI Development Center} % Organization
    {Minsk, Belarus} % Location
    {Jun. 2003 - Nov. 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of WinForms product for rapid design of optical transport networks.}
        \item {Implemented an XSLT-based templating engine to transform XML data into SVG equipment images.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior C++ Developer} % Job title
    {Coherent Solutions} % Organization
    {Minsk, Belarus} % Location
    {Mar. 2002 - Jun. 2003} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Online community portal featuring news aggregator, groups organizer and events planner in C++ and HTML.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
